```{r setup}
knitr::opts_knit$set(root.dir = "~/JishnuLab/ABomics_cleaned/Analyses")
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r}
# load libraries
library(RColorBrewer)
library(ComplexHeatmap)
library(circlize)
library(dplyr)
library(tidyr)
library(readr)
library(corrplot)
```

#### load patient & ag datasets
```{r}
source("antigens/plotting_codes/plotting_helper_fxns.R")
source("load_data.R") # patient matrices, check filepaths

# Load required data - antigen matrices 
full_ag_matrix <- readRDS("antigens/ag_data/full_feat_ag_matrix.rds")
probe_df <- data.frame("Probe" = remove_suffix(row.names(full_ag_matrix)), full_ag_matrix)

# Aggregate full ag matrix by probe
aggregated_matrix <- probe_df %>%
  group_by(Probe) %>%
  summarise(across(everything(), sum)) %>%
  as.data.frame()
  rownames(aggregated_matrix) <- aggregated_matrix$Probe
  aggregated_matrix <- aggregated_matrix[,-1]
 
# reference colors (yellow = NR / pink = R)   
colors = c("#EECA59", "#CA4F73") 
```


# EARLY PLOTS

####  prepare data for early plots & change file paths if necessary
```{r}
# load slide sig genes table
early_sig_path = "~/JishnuLab/ABomics_cleaned/FINAL_MODELS/Abomics/Early/SLIDE/plotSigGenes_data.RDS"
early_table <- readRDS(early_sig_path)

# Load early patient ag data 
early_ag_data <- readRDS("antigens/ag_data/patient_early_ag_data.rds")

# Load early enrichment results
early_ABMR_enrich <- read_csv("antigens/enrichment_results/Ag_earlyABMR.hypergeomV2.csv")
early_NR_enrich <- read_csv("antigens/enrichment_results/Ag_earlyNR.hypergeomV2.csv")

# Create early enrichment ag matrices (includes all ags)
early_matrices <- get_enrich_matrices(aggregated_matrix, early_ABMR_enrich, early_NR_enrich)

# create annotation table for early patients
annotation_table_early <- data.frame(
  Antigen = c(early_ag_data$set_NR, early_ag_data$shared, early_ag_data$set_R),
  Label = c(rep("NR DSAs", length(early_ag_data$set_NR)),
            rep("Shared", length(early_ag_data$shared)),
            rep("Rejector DSAs", length(early_ag_data$set_R)))
)

# get early ag and probe names
early_ag <- colnames(early_matrices$enrich_mtx)
early_probe <- rownames(early_matrices$enrich_mtx)

# filter ag matrix, selects ag only found in early patients 
early_ag_full <- full_ag_matrix[, early_ag]

# filter matrix by early SIG LF features 
early_siglf_feats <- unique(na.omit(early_table$names))
early_ag_matrix <- early_ag_full[early_siglf_feats,] 
early_matrices_lf <- get_enrich_matrices_lf(early_ag_matrix, early_ABMR_enrich, early_NR_enrich)
```

#### EARLY: Probe - antigen AGGREGATED plot
```{r}
# create factor to indicate if an antigen is present in the historical data
hist_type_early <- annotation_table_early[match(colnames(early_matrices$enrich_mtx), annotation_table_early$Antigen),]$Label
hist_type_early[is.na(hist_type_early)] <- "Non-DSA"
hist_type_early <- factor(hist_type_early, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Heatmap annotation for early patient DSAs
ha_co_early <- HeatmapAnnotation(
  early = hist_type_early,
  col = list(early = c("Shared" = "darkorange", "Rejector DSAs" = colors[2], "NR DSAs" = colors[1], "Non-DSA" = "lightgrey")),
  which = "column", annotation_label = "early Patient DSAs",
  show_annotation_name = FALSE, show_legend = TRUE
)

# Create heatmap for early enrichment
# early matrices
Heatmap(
  early_matrices$enrich_mtx, 
  col = c("white", "#CFD6DC"), name = "counts", 
  show_row_dend = FALSE, show_column_dend = FALSE,
  cluster_columns = FALSE, cluster_rows = TRUE,
  column_split = hist_type_early,
  top_annotation = ha_co_early,
  column_gap = unit(1, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_gp = gpar(fontsize = 10), row_names_side = "left",
  row_title = "Probes", row_title_side = "left",
  column_names_gp = gpar(fontsize = 10),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (early_matrices$highlight_ABMR[i, j] < 0) grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    if (early_matrices$highlight_NR[i, j] < 0) grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
  }
)
```


#### EARLY: SLIDE probe-ag highlighted (all early lfs)
```{r}
#############################
# Plotting all early lf_feats
#############################
# Recode colors for early probes
early_colors <- recode(early_table[match(row.names(early_matrices_lf$enrich_mtx), early_table$names),]$color, 
                       "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

# Annotate for early lf  matrices
hist_type <- annotation_table_early[match(colnames(early_matrices_lf$enrich_mtx), annotation_table_early$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type <- factor(hist_type, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Create annotations for heatmap (column and row annotations)
column_annotation <- HeatmapAnnotation(
  early = hist_type,
  col = list(early = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "Early DSAs",
  show_annotation_name = TRUE
)
# Row annotation corresponds to SLIDE results
row_annotation <- HeatmapAnnotation(
  SLIDE = early_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row"
)

# Extract probe names and antigen types
early_probes <- remove_suffix(rownames(early_matrices_lf$enrich_mtx))
antigen_types <- extract_letters(colnames(early_matrices_lf$enrich_mtx))

# Plot heatmap -- early matrices lf 
Heatmap(
  early_matrices_lf$enrich_mtx,
  column_split = hist_type,
  col = c("white", "#CFD6DC"),
  name = "Ag present \n or absent",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  #row_split = early_probes,
  top_annotation = column_annotation, # COLUMN ANNOTATION
  #left_annotation = row_annotation, 
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (early_matrices_lf$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (early_matrices_lf$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
```

#### EARLY: SLIDE probe-antigen highlighted - IgM and SNA
```{r}
#############################
# Plotting IgM and SNA only
#############################

filtered_matrices <- lapply(early_matrices_lf, function(matrix) {
  matrix[grepl("^(IgM|SNA)", rownames(matrix)), , drop = FALSE]
})

# Recode colors for early probes and 
early_colors <- recode(early_table[match(row.names(filtered_matrices$enrich_mtx), early_table$names),]$color, "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

# Create annotation for FILTERED early matrices
hist_type <- annotation_table_early[match(colnames(filtered_matrices$enrich_mtx), annotation_table_early$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type <- factor(hist_type, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Create annotations for heatmap (column and row annotations)
column_annotation <- HeatmapAnnotation(
  early = hist_type,
  col = list(early = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "Early DSAs",
  show_legend = FALSE
)

row_annotation <- HeatmapAnnotation(
  SLIDE = early_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row",  show_legend = FALSE
)

# Extract probe names and antigen types
early_probes <- remove_suffix(rownames(filtered_matrices$enrich_mtx))
antigen_types <- extract_letters(colnames(filtered_matrices$enrich_mtx))

# Plot heatmap for IgM and SNA 
e_lf_hm <- Heatmap(
  filtered_matrices$enrich_mtx,
  column_split = hist_type_early,
  col = c("white", "#CFD6DC"),
  name = "Ag present \n or absent",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  row_split = early_probes,
  top_annotation = column_annotation, 
  left_annotation = row_annotation,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (filtered_matrices$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (filtered_matrices$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
e_lf_hm
```

##### corr plots for IGM/SNA heatmaps
```{r}
e_f = rownames(filtered_matrices$enrich_mtx)
earlyNR_ef <- early_r %>% select(e_f) # non rejectors
earlyR_ef <- early_nr %>% select(e_f) # non rejectors

# plots
p1_NR <- AB_heatmap(earlyNR_ef)
p2_R <-  AB_heatmap(earlyR_ef)
draw(p1_NR + p2_R, column_title = " Early Non Rejectors vs. Early Rejectors ", ht_gap = unit(0.5, "cm"))

# combine heatmap with corrplots 
# folder = "antigens/figures/early_3plot.pdf"
# pdf(folder, width = 13, height = 4)  # Specify file name and dimensions
# draw(e_lf_hm +  p1_NR + p2_R, ht_gap = unit(0.5, "cm"))  # Plot the heatmap to the PDF
# dev.off()  # Close the PDF device
# # # # 
```

# LATE PLOTS

#### prepare data for late plots & change file paths if necessary
```{r}
# get late sig lfs
late_sig_path = "~/JishnuLab/ABomics_cleaned/FINAL_MODELS/Abomics/late/SLIDE/plotSigGenes_data.RDS"
late_table <- readRDS(late_sig_path)
late_siglf_feats <- unique(na.omit(late_table$names))

# Load enrichment results
late_ABMR_enrich <- read_csv("antigens/enrichment_results/Ag_lateABMR.hypergeomV2.csv")
late_NR_enrich <- read_csv("antigens/enrichment_results/Ag_lateNR.hypergeomV2.csv")

# Load late patient data and create annotation table
late_ag_data <- readRDS("antigens/ag_data/patient_late_ag_data.rds")
annotation_table_late <- data.frame(
  Antigen = c(late_ag_data$set_NR, late_ag_data$shared, late_ag_data$set_R),
  Label = c(rep("NR DSAs", length(late_ag_data$set_NR)),
            rep("Shared", length(late_ag_data$shared)),
            rep("Rejector DSAs", length(late_ag_data$set_R))))

# Generate late enrichment matrices
late_matrices <- get_enrich_matrices(aggregated_matrix, late_ABMR_enrich, late_NR_enrich)

# Extract relevant columns and rows
late_ag <- colnames(late_matrices$enrich_mtx)
late_probe <- rownames(late_matrices$enrich_mtx)
late_ag_full <- full_ag_matrix[, late_ag] # late ag matrix 

# Filter matrix by sig lfs
late_ag_matrix <- late_ag_full[late_siglf_feats,]
# late enrichment sig lf matrices
late_matrices_lf <- get_enrich_matrices_lf(late_ag_matrix, late_ABMR_enrich, late_NR_enrich)
```

#### LATE: Probe-antigen aggregated
```{r}
# Annotate late matrices
hist_type_late <- annotation_table_late[match(colnames(late_matrices$enrich_mtx), annotation_table_late$Antigen),]$Label
hist_type_late[is.na(hist_type_late)] <- "Non-DSA"
hist_type_late <- factor(hist_type_late, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Heatmap annotation for late patient DSAs
ha_co_late <- HeatmapAnnotation(
  late = hist_type_late,
  col = list(late = c("Shared" = "darkorange", "Rejector DSAs" = colors[2], "NR DSAs" = colors[1], "Non-DSA" = "lightgrey")),
  which = "column", annotation_label = "late Patient DSAs",
  show_annotation_name = FALSE, show_legend = TRUE
)

# Create heatmap for late enrichment
# late_matrices
Heatmap(
  late_matrices$enrich_mtx, 
  col = c("white", "#CFD6DC"), name = "counts", 
  show_row_dend = FALSE, show_column_dend = FALSE,
  cluster_columns = FALSE, cluster_rows = TRUE,
  column_split = hist_type_late,
  top_annotation = ha_co_late,
  column_gap = unit(1, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_gp = gpar(fontsize = 10), row_names_side = "left",
  row_title = "Probes", row_title_side = "left",
  column_names_gp = gpar(fontsize = 10),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (late_matrices$highlight_ABMR[i, j] < 0) grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    if (late_matrices$highlight_NR[i, j] < 0) grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
  }
)

```


#### LATE: SLIDE Probe - antigen highighted (all late lfs)
```{r}
#############################
# Plotting all late_feats
#############################

# Recode colors for late probes 
late_colors <- recode(late_table[match(row.names(late_matrices_lf$enrich_mtx), late_table$names),]$color, "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

# Annotate late matrices
hist_type_late <- annotation_table_late[match(colnames(late_matrices_lf$enrich_mtx), annotation_table_late$Antigen),]$Label
hist_type_late[is.na(hist_type_late)] <- "Non-DSA"
hist_type_late <- factor(hist_type_late, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Create annotations for heatmap (column and row annotations)
column_annotation <- HeatmapAnnotation(
  late = hist_type_late,
  col = list(late = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "late DSAs",
  show_annotation_name = TRUE
)

row_annotation <- HeatmapAnnotation(
  SLIDE = late_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row"
)

# Extract probe names and antigen types
late_probes <- remove_suffix(rownames(late_matrices_lf$enrich_mtx))
antigen_types <- extract_letters(colnames(late_matrices_lf$enrich_mtx))

Heatmap(
  late_matrices_lf$enrich_mtx,
  column_split = hist_type_late,
  col = c("white", "#CFD6DC"),
  name = "Ag present \n or absent",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  top_annotation = column_annotation,
  #left_annotation = row_annotation,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (late_matrices_lf$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (late_matrices_lf$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
```

#### LATE: SLIDE probe-antigen highlighted - FCR3A IgG / dp, DQ9, DR53, DR8
```{r}
#############################
# Plotting FcR3A IgGonly
#############################

filt_mat_late <- lapply(late_matrices_lf, function(x) {
  rows_to_keep <- grepl("^(FcR3A|IgG_)", rownames(x))
  cols_to_keep<- grepl("^(DP)|^DQ9|^DR53|^DR8", colnames(x))
  x[rows_to_keep,cols_to_keep, drop = FALSE]
  
})

# Recode colors for late probes and create factor for historical data
late_colors <- recode(late_table[match(row.names(filt_mat_late$enrich_mtx), late_table$names),]$color,  "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

hist_type <- annotation_table_late[match(colnames(filt_mat_late$enrich_mtx), annotation_table_late$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type <- factor(hist_type, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Create annotations for heatmap (column and row annotations)
col_late <- HeatmapAnnotation(
  late = hist_type,
  col = list(late = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "late DSAs",
  show_legend = FALSE
)
# row annotations correspond to SLIDE results
row_late <- HeatmapAnnotation(
  SLIDE = late_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row",  show_legend = FALSE
)

# Extract probe names and antigen types
late_probes <- remove_suffix(rownames(filt_mat_late$enrich_mtx))
antigen_types <- extract_letters(colnames(filt_mat_late$enrich_mtx))

# Plot heatmap 
l_lf_hm <- Heatmap(
  filt_mat_late$enrich_mtx,
  column_split = hist_type,
  col = c("white", "#CFD6DC"),
  name = "Ag present \n or absent",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  row_split = late_probes,
  top_annotation = col_late,
  left_annotation = row_late,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (filt_mat_late$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (filt_mat_late$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
l_lf_hm
```


##### combining enrichment heatmap with corrplots
```{r}
l_f = rownames(filt_mat_late$enrich_mtx)
lateNR_lf <- late_nr %>% select(l_f) # non rejectors
lateR_lf <- early_nr %>% select(l_f) # rejectors

# corr plots
p1_NR <- AB_heatmap(lateNR_lf)
p2_R <-  AB_heatmap(lateR_lf)
draw(p1_NR + p2_R, column_title = " late Non Rejectors vs. late Rejectors ",ht_gap = unit(0.5, "cm"))

# folder = "antigens/figures/late_fcrIgG_3plot.pdf"
# pdf(folder, width = 9.5, height = 4)  
# draw(l_lf_hm +  p1_NR + p2_R, ht_gap = unit(0.5, "cm"))  # Plot the heatmap to the PDF
# dev.off()  
```


#### LATE: SLIDE probe-antigen highlighted - IgM C1Q / A ags
```{r}
#############################
# Plotting IgM C1Q
#############################

filt_mat_late <- lapply(late_matrices_lf, function(x) {
  rows_to_keep <- grepl("^(IgM|C1Q)", rownames(x))   # Get only IGM and C1Q 
  cols_to_keep <- grepl("^(A)", colnames(x))   # Get only A Ag
  x[rows_to_keep, cols_to_keep, drop = FALSE]
})

# Recode colors for late probes and create factor for historical data
late_colors <- recode(late_table[match(row.names(filt_mat_late$enrich_mtx), late_table$names),]$color, "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

hist_type <- annotation_table_late[match(colnames(filt_mat_late$enrich_mtx), annotation_table_late$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type <- factor(hist_type, levels = c("Non-DSA", "NR DSAs", "Rejector DSAs", "Shared"))

# Create annotations for heatmap (column and row annotations)
col_late <- HeatmapAnnotation(
  late = hist_type,
  col = list(late = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "late DSAs",
 show_legend = FALSE
)

row_late <- HeatmapAnnotation(
  SLIDE = late_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row",  show_legend = FALSE
)

# Extract probe names and antigen types
late_probes <- remove_suffix(rownames(filt_mat_late$enrich_mtx))
antigen_types <- extract_letters(colnames(filt_mat_late$enrich_mtx))

# Plot heatmap for IgM and SNA
l_lf_hm <- Heatmap(
  filt_mat_late$enrich_mtx,
  column_split = hist_type,
  col = c("white", "#CFD6DC"),
  name = "Ag present \n or absent",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  row_split = late_probes,
  top_annotation = col_late,
  left_annotation = row_late,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (filt_mat_late$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (filt_mat_late$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
l_lf_hm
```

##### combining enrichment heatmap  corrplots
```{r}
l_f = rownames(filt_mat_late$enrich_mtx)
lateNR_lf <- late_nr %>% select(l_f) # non rejectors
lateR_lf <- early_nr %>% select(l_f) # non rejectors

# plots
p1_NR<- AB_heatmap(lateNR_lf, thresh = 0.01)
p2_R <-  AB_heatmap(lateR_lf, thresh = 0.01)
draw(p1_NR + p2_R, column_title = " late Non Rejectors vs. late Rejectors ",ht_gap = unit(0.5, "cm"))

#folder = "antigens/figures/late_c1qigm_3plot_test.pdf"
#pdf(folder, width = 14, height = 5.5)  
#draw(l_lf_hm +  p1_NR + p2_R, ht_gap = unit(0.5, "cm"))  # Plot the heatmap to the PDF
#dev.off()  
```


