```{r}
# ~/JishnuLab/ABomics_cleaned/Analyses/antigens/plotting_codes/enrichment_early_simplified.R

setwd("~/JishnuLab/ABomics_cleaned/")
#source("Analyses/correlation/Z_score_cocor.R")
source("Analyses/correlation/Helper_fx.R")
source("Analyses/load_data.R")
source("~/JishnuLab/ABomics_cleaned/Analyses/antigens/plotting_codes/Plotting_helper_fxns.R")
colors = c("#EECA59", "#CA4F73")

library(RColorBrewer)
library(ComplexHeatmap)
library(circlize)
library(dplyr)
library(tidyr)
library(readr)
library(Hmisc)
library(corrplot)

### function for pval stars #####################
labs.function <- function(x) {
  case_when(
    is.na(x) ~ "",  
    x == 0 ~ "",       # Return an empty string for NA values
    # Return an empty string for NA values
    x >= 0.05 ~ "",      # No asterisk for p-values >= 0.05
    x < 0.05 & x >= 0.01 ~ "*",    # One asterisk for p-values < 0.05 and >= 0.01
    x < 0.01 & x >= 0.001 ~ "**",  # Two asterisks for p-values < 0.01 and >= 0.001
    x < 0.001 ~ "***"    # Three asterisks for p-values < 0.001
  )
}

### corr m ptest ################################################
cor.mtest <- function(mat, ...) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat<- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j], ...)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}

### corrplot fx ################################################
AB_corrplot <- function(data, thresh){
  col_fun <- colorRamp2(c(-1, 0, 1), c("blue", "white", "red"))
  M <- cor(data, method = "spearman")
  p.mat <- cor.mtest(data, method = "spearman", exact = NULL)
  # Specialized the insignificant value according to the significant level
  plot <- corrplot(M, type="lower", insig = "label_sig", diag= F,
                 p.ma = p.mat, sig.level = thresh,col = col_fun,
                # cl.lim=c(-1,0,1), col=colorRampPalette(c("blue","white","red")(200)),
                 tl.col="black", tl.srt=45 )
  plot
}

##################################################################################
AB_heatmap<- function(sub, thresh = NULL){
  corr_mat <- cor(scale(sub), method = 'spearman')
  col_fun <- colorRamp2(c(-1, 0, 1), c("blue", "white", "red"))
  
  probes_c = remove_suffix(colnames(corr_mat))
  probes_r = remove_suffix(rownames(corr_mat))
  p_mat <- cor.mtest(corr_mat, method = "spearman", exact = NULL)
  corr_mat[p_mat > thresh |is.na(p_mat)] <- NA
  
  if(is.null(thresh)){
    
    asterisk_matrix <- apply(p_mat, MARGIN = c(1, 2), labs.function)
    heatmap <- Heatmap(
      corr_mat,
      col = col_fun,
      name = "Spearman \n correlation",
      row_split = probes_r,
      column_split = probes_c, 
      show_row_dend = FALSE,
      show_column_dend = FALSE,
      cluster_columns = FALSE,
      cluster_rows = FALSE,
      na_col = "#ededed",
      rect_gp = gpar(col = "black", lwd = 1),
      #cell_fun = draw_asterisks , # Add the custom function for asterisks
      row_title_rot = 0
    ) 
    heatmap
  }else{ heatmap <- Heatmap(
      corr_mat,
      col = col_fun,
      name = "Spearman \n correlation",
      row_split = probes_r,
      column_split = probes_c, 
      show_row_dend = FALSE,
      show_column_dend = FALSE,
      cluster_columns = FALSE,
      cluster_rows = FALSE,
      na_col = "#ededed",
      rect_gp = gpar(col = "black", lwd = 1),
      row_title_rot = 0)
    heatmap
  }
}

# load datasets
X1 = early_r
X2 = early_nr
X3 = late_r
X4 = late_nr
r_group = rbind(X1, X3)
nr_group = rbind(X2, X4)

early_group = rbind(X1, X2)
late_group = rbind(X3, X4)
```


#EARLY: Probe - antigen aggregated
```{r}
# Load required data
setwd("~/JishnuLab/ABomics_cleaned/Analyses/antigens/")

full_ag_matrix <- readRDS("ag_data/full_feat_ag_matrix.rds")
probe_df <- data.frame("Probe" = remove_suffix(row.names(full_ag_matrix)), full_ag_matrix)

# Aggregate by probe
aggregated_matrix <- probe_df %>%
  group_by(Probe) %>%
  summarise(across(everything(), sum)) %>%
  as.data.frame()

rownames(aggregated_matrix) <- aggregated_matrix$Probe
aggregated_matrix <- aggregated_matrix[,-1]

# Load enrichment data
ABMR_enrich <- read_csv("enrichment_results/Ag_earlyABMR.hypergeomV2.csv")
NR_enrich <- read_csv("enrichment_results/Ag_earlyNR.hypergeomV2.csv")

# Generate early enrichment matrices
early_matrices <- get_enrich_matrices(aggregated_matrix, ABMR_enrich, NR_enrich)

# Load early patient data and create annotation table
early_ag_data <- readRDS("ag_data/patient_early_ag_data.rds")
annotation_table_early <- data.frame(
  Antigen = c(early_ag_data$set_NR, early_ag_data$shared, early_ag_data$set_R),
  Label = c(rep("NR DSAs", length(early_ag_data$set_NR)),
            rep("Shared", length(early_ag_data$shared)),
            rep("Rejector DSAs", length(early_ag_data$set_R)))
)

# Annotate early matrices
hist_type_early <- annotation_table_early[match(colnames(early_matrices$enrich_mtx), annotation_table_early$Antigen),]$Label
hist_type_early[is.na(hist_type_early)] <- "Non-DSA"
hist_type_factor_early <- factor(hist_type_early, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Heatmap annotation for early patient DSAs
ha_co_early <- HeatmapAnnotation(
  early = hist_type_factor_early,
  col = list(early = c("Shared" = "darkorange", "Rejector DSAs" = colors[2], "NR DSAs" = colors[1], "Non-DSA" = "lightgrey")),
  which = "column", annotation_label = "early Patient DSAs",
  show_annotation_name = FALSE, show_legend = TRUE
)

# Create heatmap for early enrichment
Heatmap(
  early_matrices$enrich_mtx, 
  col = c("white", "#CFD6DC"), name = "counts", 
  show_row_dend = FALSE, show_column_dend = FALSE,
  cluster_columns = FALSE, cluster_rows = TRUE,
  column_split = hist_type_factor_early,
  top_annotation = ha_co_early,
  column_gap = unit(1, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_gp = gpar(fontsize = 10), row_names_side = "left",
  row_title = "Probes", row_title_side = "left",
  column_names_gp = gpar(fontsize = 10),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (early_matrices$highlight_ABMR[i, j] < 0) grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    if (early_matrices$highlight_NR[i, j] < 0) grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
  }
)

```

#EARLY: SLIDE probe-ag full
```{r}
# Extract relevant columns and rows
early_ag <- colnames(early_matrices$enrich_mtx)
early_probe <- rownames(early_matrices$enrich_mtx)

# Filter full antigen matrix and load features
early_ag_full <- full_ag_matrix[, early_ag]
early_table <- readRDS("~/JishnuLab/ABomics_cleaned/FINAL_MODELS/Abomics/Early/SLIDE/plotSigGenes_data.RDS")
early_feats <- unique(na.omit(early_table$names))

# Filter matrix by features
early_ag_matrix <- early_ag_full[early_feats,]
# Highlight probes
# Generate low-frequency early enrichment matrices (IgM, SNA filtering)
early_matrices_lf <- get_enrich_matrices_lf(early_ag_matrix, ABMR_enrich, NR_enrich)

#############################
# Plotting all early_feats
#############################


# Recode colors for early probes and create histology type factor
early_colors <- recode(early_table[match(row.names(early_matrices_lf$enrich_mtx), early_table$names),]$color, 
                       "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

hist_type <- annotation_table_early[match(colnames(early_matrices_lf$enrich_mtx), annotation_table_early$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type_factor <- factor(hist_type, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Create annotations for heatmap (column and row annotations)
column_annotation <- HeatmapAnnotation(
  early = hist_type_factor,
  col = list(early = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "early DSAs",
  show_annotation_name = TRUE
)

row_annotation <- HeatmapAnnotation(
  SLIDE = early_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row"
)

# Extract probe names and antigen types
early_probes <- remove_suffix(rownames(early_matrices_lf$enrich_mtx))
antigen_types <- extract_letters(colnames(early_matrices_lf$enrich_mtx))

# Plot heatmap for IgM and SNA
Heatmap(
  early_matrices_lf$enrich_mtx,
  column_split = hist_type_early,
  col = c("white", "#CFD6DC"),
  name = "counts",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  #row_split = early_probes,
  top_annotation = ha_col_early,
  #left_annotation = ha_row_earlylf,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (early_matrices_lf$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (early_matrices_lf$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
```

# EARLY: SLIDE probe-antigen highlighted - selected
```{r}
# Extract relevant columns and rows
early_ag <- colnames(early_matrices$enrich_mtx)
early_probe <- rownames(early_matrices$enrich_mtx)

# Filter full antigen matrix and load features
early_ag_mtx <- full_ag_matrix[, early_ag]
early_table <- readRDS("~/JishnuLab/ABomics_cleaned/FINAL_MODELS/Abomics/Early/SLIDE/plotSigGenes_data.RDS")
early_feats <- unique(na.omit(early_table$names))

# Filter matrix by features
early_ag_matrix <- early_ag_mtx[early_feats,]
# Highlight probes
# Generate low-frequency early enrichment matrices (IgM, SNA filtering)
early_matrices_lf <- get_enrich_matrices_lf(early_ag_matrix, ABMR_enrich, NR_enrich)

#############################
# Plotting IgM and SNA only
#############################

filtered_matrices <- lapply(early_matrices_lf, function(matrix) {
  matrix[grepl("^(IgM|SNA)", rownames(matrix)), , drop = FALSE]
})


# Recode colors for early probes and create histology type factor
early_colors <- recode(early_table[match(row.names(filtered_matrices$enrich_mtx), early_table$names),]$color, 
                       "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

hist_type <- annotation_table_early[match(colnames(filtered_matrices$enrich_mtx), annotation_table_early$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type_factor <- factor(hist_type, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Create annotations for heatmap (column and row annotations)
column_annotation <- HeatmapAnnotation(
  early = hist_type_factor,
  col = list(early = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "early DSAs",
 show_legend = FALSE
)

row_annotation <- HeatmapAnnotation(
  SLIDE = early_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row",  show_legend = FALSE
)

# Extract probe names and antigen types
early_probes <- remove_suffix(rownames(filtered_matrices$enrich_mtx))
antigen_types <- extract_letters(colnames(filtered_matrices$enrich_mtx))

# Plot heatmap for IgM and SNA
e_lf_hm <- Heatmap(
  filtered_matrices$enrich_mtx,
  column_split = hist_type_early,
  col = c("white", "#CFD6DC"),
  name = "counts",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  row_split = early_probes,
  top_annotation = ha_col_early,
  left_annotation = ha_row_earlylf,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (filtered_matrices$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (filtered_matrices$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
e_lf_hm
```
# EARLY (early_feats) individual corr plots
```{r}
e_f = rownames(filtered_matrices$enrich_mtx)
earlyNR_ef <- X2 %>% select(e_f) # non rejectors
earlyR_ef <- X1 %>% select(e_f) # non rejectors

# plots
p1_NR<- AB_heatmap(earlyNR_ef)
p2_R <-  AB_heatmap(earlyR_ef)
draw(p1_NR + p2_R, column_title = " Early Non Rejectors vs. Early Rejectors ",ht_gap = unit(0.5, "cm"))
```

# EARLY 3 PLOTS COMBINED
```{r}
folder = "~/JishnuLab/ABomics_cleaned/Analyses/antigens/figures/early_3plot.pdf"
pdf(folder, width = 13, height = 4)  # Specify file name and dimensions
draw(e_lf_hm +  p1_NR + p2_R, ht_gap = unit(0.5, "cm"))  # Plot the heatmap to the PDF
dev.off()  # Close the PDF device
# # # 
```

# LATE: Probe-antigen aggregated
```{r}
# Load required data
setwd("~/JishnuLab/ABomics_cleaned/Analyses/antigens/")

full_ag_matrix <- readRDS("ag_data/full_feat_ag_matrix.rds")
probe_df <- data.frame("Probe" = remove_suffix(row.names(full_ag_matrix)), full_ag_matrix)

# Aggregate by probe
aggregated_matrix <- probe_df %>%
  group_by(Probe) %>%
  summarise(across(everything(), sum)) %>%
  as.data.frame()

rownames(aggregated_matrix) <- aggregated_matrix$Probe
aggregated_matrix <- aggregated_matrix[,-1]

# Load enrichment data
ABMR_enrich <- read_csv("enrichment_results/Ag_lateABMR.hypergeomV2.csv")
NR_enrich <- read_csv("enrichment_results/Ag_lateNR.hypergeomV2.csv")

# Generate late enrichment matrices
late_matrices <- get_enrich_matrices(aggregated_matrix, ABMR_enrich, NR_enrich)

# Load late patient data and create annotation table
late_ag_data <- readRDS("ag_data/patient_late_ag_data.rds")
annotation_table_late <- data.frame(
  Antigen = c(late_ag_data$set_NR, late_ag_data$shared, late_ag_data$set_R),
  Label = c(rep("NR DSAs", length(late_ag_data$set_NR)),
            rep("Shared", length(late_ag_data$shared)),
            rep("Rejector DSAs", length(late_ag_data$set_R)))
)

# Annotate late matrices
hist_type_late <- annotation_table_late[match(colnames(late_matrices$enrich_mtx), annotation_table_late$Antigen),]$Label
hist_type_late[is.na(hist_type_late)] <- "Non-DSA"
hist_type_factor_late <- factor(hist_type_late, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Heatmap annotation for late patient DSAs
ha_co_late <- HeatmapAnnotation(
  late = hist_type_factor_late,
  col = list(late = c("Shared" = "darkorange", "Rejector DSAs" = colors[2], "NR DSAs" = colors[1], "Non-DSA" = "lightgrey")),
  which = "column", annotation_label = "late Patient DSAs",
  show_annotation_name = FALSE, show_legend = TRUE
)

# Create heatmap for late enrichment
Heatmap(
  late_matrices$enrich_mtx, 
  col = c("white", "#CFD6DC"), name = "counts", 
  show_row_dend = FALSE, show_column_dend = FALSE,
  cluster_columns = FALSE, cluster_rows = TRUE,
  column_split = hist_type_factor_late,
  top_annotation = ha_co_late,
  column_gap = unit(1, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_gp = gpar(fontsize = 10), row_names_side = "left",
  row_title = "Probes", row_title_side = "left",
  column_names_gp = gpar(fontsize = 10),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (late_matrices$highlight_ABMR[i, j] < 0) grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    if (late_matrices$highlight_NR[i, j] < 0) grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
  }
)

```


#late: SLIDE probe-ag full
```{r}
# Extract relevant columns and rows
late_ag <- colnames(late_matrices$enrich_mtx)
late_probe <- rownames(late_matrices$enrich_mtx)

# Filter full antigen matrix and load features
late_ag_full <- full_ag_matrix[, late_ag]
late_table <- readRDS("~/JishnuLab/ABomics_cleaned/FINAL_MODELS/Abomics/late/SLIDE/plotSigGenes_data.RDS")
late_feats <- unique(na.omit(late_table$names))

# Filter matrix by features
late_ag_matrix <- late_ag_full[late_feats,]
# Highlight probes
# Generate low-frequency late enrichment matrices (IgM, SNA filtering)
late_matrices_lf <- get_enrich_matrices_lf(late_ag_matrix, ABMR_enrich, NR_enrich)

#############################
# Plotting all late_feats
#############################


# Recode colors for late probes and create histology type factor
late_colors <- recode(late_table[match(row.names(late_matrices_lf$enrich_mtx), late_table$names),]$color, 
                       "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

hist_type <- annotation_table_late[match(colnames(late_matrices_lf$enrich_mtx), annotation_table_late$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type_factor <- factor(hist_type, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Create annotations for heatmap (column and row annotations)
column_annotation <- HeatmapAnnotation(
  late = hist_type_factor,
  col = list(late = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "late DSAs",
  show_annotation_name = TRUE
)

row_annotation <- HeatmapAnnotation(
  SLIDE = late_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row"
)

# Extract probe names and antigen types
late_probes <- remove_suffix(rownames(late_matrices_lf$enrich_mtx))
antigen_types <- extract_letters(colnames(late_matrices_lf$enrich_mtx))

Heatmap(
  late_matrices_lf$enrich_mtx,
  column_split = hist_type_late,
  col = c("white", "#CFD6DC"),
  name = "counts",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  #row_split = early_probes,
  top_annotation =column_annotation,
  #left_annotation = ha_row_latelf,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (late_matrices_lf$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (late_matrices_lf$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
```

# LATE: SLIDE probe-antigen highlighted - FCR3A IgG
# dp, DQ9, DR53, DR8
```{r}
# Extract relevant columns and rows
late_ag <- colnames(late_matrices$enrich_mtx)
late_probe <- rownames(late_matrices$enrich_mtx)

# Filter full antigen matrix and load features
late_ag_mtx <- full_ag_matrix[, late_ag]
late_table <- readRDS("~/JishnuLab/ABomics_cleaned/FINAL_MODELS/Abomics/late/SLIDE/plotSigGenes_data.RDS")
late_feats <- unique(na.omit(late_table$names))

# Filter matrix by features
late_ag_matrix <- late_ag_mtx[late_feats,]
# Highlight probes
# Generate low-frequency late enrichment matrices (IgM, SNA filtering)
late_matrices_lf <- get_enrich_matrices_lf(late_ag_matrix, ABMR_enrich, NR_enrich)

#############################
# Plotting FcR3A IgGonly
#############################

filt_mat_late <- lapply( late_matrices_lf, function(x) {
  # Get row names that start with "IGM"
  rows_to_keep <- grepl("^(FcR3A|IgG_)", rownames(x))
  #rows_to_keep <- grepl("^(IgM|C1Q)", rownames(x))
  # Subset the matrix to keep only these rows
  # Get column names that start with "A", "B", or "C"
  cols_to_keep <- grepl("^(DP)", colnames(x))
  ag_keep = c("DQ9", "DR53", "DR8")
  # Subset the matrix to keep only these rows and columns
  x[rows_to_keep,c(cols_to_keep, ag_keep), drop = FALSE]
  
})

# filt_mat_late <- lapply(late_matrices_lf, function(matrix) {
#   matrix[grepl("^(FcR3A|IgG_)", rownames(matrix)), , drop = FALSE]
# })


# Recode colors for late probes and create histology type factor
late_colors <- recode(late_table[match(row.names(filt_mat_late$enrich_mtx), late_table$names),]$color, 
                       "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

hist_type <- annotation_table_late[match(colnames(filt_mat_late$enrich_mtx), annotation_table_late$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type_factor <- factor(hist_type, levels = c("Non-DSA", "Shared", "Rejector DSAs", "NR DSAs"))

# Create annotations for heatmap (column and row annotations)
col_late <- HeatmapAnnotation(
  late = hist_type_factor,
  col = list(late = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "late DSAs",
 show_legend = FALSE
)

row_late <- HeatmapAnnotation(
  SLIDE = late_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row",  show_legend = FALSE
)

# Extract probe names and antigen types
late_probes <- remove_suffix(rownames(filt_mat_late$enrich_mtx))
antigen_types <- extract_letters(colnames(filt_mat_late$enrich_mtx))

# Plot heatmap for IgM and SNA
l_lf_hm <- Heatmap(
  filt_mat_late$enrich_mtx,
  column_split = hist_type_factor,
  col = c("white", "#CFD6DC"),
  name = "counts",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  row_split = late_probes,
  top_annotation = col_late,
  left_annotation = row_late,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (filt_mat_late$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (filt_mat_late$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
l_lf_hm
```
# LATE (fcr igg) individual corr plots / 3 plots combined
```{r}
l_f = rownames(filt_mat_late$enrich_mtx)
lateNR_lf <- X4 %>% select(l_f) # non rejectors
lateR_lf <- X3 %>% select(l_f) # non rejectors

# plots
p1_NR<- AB_heatmap(lateNR_lf)
p2_R <-  AB_heatmap(lateR_lf)
#draw(p1_NR + p2_R, column_title = " late Non Rejectors vs. late Rejectors ",ht_gap = unit(0.5, "cm"))


folder = "~/JishnuLab/ABomics_cleaned/Analyses/antigens/figures/late_fcrIgG_3plot.pdf"
pdf(folder, width = 9.5, height = 4)  # Specify file name and dimensions
draw(l_lf_hm +  p1_NR + p2_R, ht_gap = unit(0.5, "cm"))  # Plot the heatmap to the PDF
dev.off()  # Close the PDF device
# # # 
```


# LATE: IgG IGM
# LATE: SLIDE probe-antigen highlighted - igm c1q
```{r}
# Extract relevant columns and rows
late_ag <- colnames(late_matrices$enrich_mtx)
late_probe <- rownames(late_matrices$enrich_mtx)

# Filter full antigen matrix and load features
late_ag_mtx <- full_ag_matrix[, late_ag]
late_table <- readRDS("~/JishnuLab/ABomics_cleaned/FINAL_MODELS/Abomics/late/SLIDE/plotSigGenes_data.RDS")
late_feats <- unique(na.omit(late_table$names))

# Filter matrix by features
late_ag_matrix <- late_ag_mtx[late_feats,]
# Highlight probes
# Generate low-frequency late enrichment matrices (IgM, SNA filtering)
late_matrices_lf <- get_enrich_matrices_lf(late_ag_matrix, ABMR_enrich, NR_enrich)

#############################
# Plotting FcR3A IgGonly
#############################

filt_mat_late <- lapply( late_matrices_lf, function(x) {
  # Get row names that start with "IGM"
  rows_to_keep <- grepl("^(IgM|C1Q)", rownames(x))
  # Subset the matrix to keep only these rows
  #cols_to_keep <- grepl("^(DP)", colnames(x))
    cols_to_keep <- grepl("^(A)", colnames(x))

  # Subset the matrix to keep only these rows and columns
  x[rows_to_keep, cols_to_keep, drop = FALSE]
  
})


# Recode colors for late probes and create histology type factor
late_colors <- recode(late_table[match(row.names(filt_mat_late$enrich_mtx), late_table$names),]$color, 
                       "Blue" = "NR", "Red" = "Rejector", 'white' = "Non-DSA")

hist_type <- annotation_table_late[match(colnames(filt_mat_late$enrich_mtx), annotation_table_late$Antigen),]$Label
hist_type[is.na(hist_type)] <- "Non-DSA"
hist_type_factor <- factor(hist_type, levels = c("Non-DSA", "NR DSAs", "Rejector DSAs", "Shared"))

# Create annotations for heatmap (column and row annotations)
col_late <- HeatmapAnnotation(
  late = hist_type_factor,
  col = list(late = c("Shared" = "darkorange", "Rejector DSAs" = "#CA4F73", "NR DSAs" = "#eebc59", "Non-DSA" = "lightgray")),
  which = "column",
  annotation_label = "late DSAs",
 show_legend = FALSE
)

row_late <- HeatmapAnnotation(
  SLIDE = late_colors,
  col = list(SLIDE = c("NR" = colors[1], "Rejector" = colors[2], "Non-DSA" = "lightgray")),
  which = "row",  show_legend = FALSE
)

# Extract probe names and antigen types
late_probes <- remove_suffix(rownames(filt_mat_late$enrich_mtx))
antigen_types <- extract_letters(colnames(filt_mat_late$enrich_mtx))

# Plot heatmap for IgM and SNA
l_lf_hm <- Heatmap(
  filt_mat_late$enrich_mtx,
  column_split = hist_type_factor,
  col = c("white", "#CFD6DC"),
  name = "counts",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_columns = FALSE,
  cluster_rows = TRUE,
  row_split = late_probes,
  top_annotation = col_late,
  left_annotation = row_late,
  column_gap = unit(3, "mm"),
  rect_gp = gpar(col = "black", lwd = 1),
  row_names_side = "left",
  row_names_gp = gpar(fontsize = 10),
  column_names_gp = gpar(fontsize = 12),
  cell_fun = function(j, i, x, y, width, height, fill) {
    grid.rect(x, y, width, height, gp = gpar(fill = fill, col = "black"))
    if (filt_mat_late$highlight_ABMR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[2], col = "black"))
    }
    if (filt_mat_late$highlight_NR[i, j] < 0) {
      grid.rect(x, y, width, height, gp = gpar(fill = colors[1], col = "black"))
    }
  }
)
l_lf_hm
```
# LATE (fcr igg) individual corr plots / 3 plots combined
```{r}
l_f = rownames(filt_mat_late$enrich_mtx)
lateNR_lf <- X4 %>% select(l_f) # non rejectors
lateR_lf <- X3 %>% select(l_f) # non rejectors

# plots
p1_NR<- AB_heatmap(lateNR_lf, thresh = 0.01)
p2_R <-  AB_heatmap(lateR_lf, thresh = 0.01)
#draw(p1_NR + p2_R, column_title = " late Non Rejectors vs. late Rejectors ",ht_gap = unit(0.5, "cm"))


folder = "~/JishnuLab/ABomics_cleaned/Analyses/antigens/figures/late_c1qigm_3plot.pdf"
pdf(folder, width = 14, height = 5.5)  # Specify file name and dimensions
draw(l_lf_hm +  p1_NR + p2_R, ht_gap = unit(0.5, "cm"))  # Plot the heatmap to the PDF
dev.off()  # Close the PDF device
# # # 
```


